\documentclass[]{article}
\title{EASY}
\date{}
\usepackage{setspace}
\pdfpagewidth 8.5in
\pdfpageheight 11in
\begin{document}
	\maketitle
	\thispagestyle{empty}
	\onehalfspacing
The newspaper can call you a `legend', in quotes and everything, but it's a Catch-22. Before anything happens, you're just the same as any other depressed kid who can draw better than you can pay attention in class -- and trust me, there are a lot of us. Even when the cops add it all up, somehow, and produce this ridiculous number -- more than half a million dollars -- you're not a legend. You're stil the same depressed kid, who can draw better than you can pay attention in class, but now look where you're at: locked up. Only when some reporter shoves a mic in the face of some detective do you suddenly become the stuff of `legends'.

Don't get me wrong. Derrick was good, real talented, and he got up, and often. But he wasn't a legend until they said he was.

These kinds of articles, they almost write themselves. Make sure it has all the right words to conjure up the stereotypical image: ``graffiti writer'', ``turf'', ``tag'', then, ``damage'', ``criminal'', ``trespassing'', ``felony''. Follow it up with a ``correctional institution'' for good measure. He likely couldn't paint you a better mental picture himself. Problem is, Derrick is nothing like what you're probably imagining. 

First of all, he's white. Real white -- red hair and freckles on pale skin white -- and when you're only out when the sun's down, you're only getting whiter. Blue eyes too, bright enough that they showed up in the grainy mugshot. Pink, chapped lips, and sparse, unshaven facial hair. True ginger.

More than appearances though, most people will try and pigeon-hole the motivation behind the criminal. You picture `thug' and you figure they just want to `fuck shit up,' but even serial arsonist's don't do it because they're trying to ruin some property. I know you've stared into a campfire long enough to know that.

The truth is, graffiti artists have figured out immortality, but they're too broke to ever really become immortal.

Think about it. Gustave Eiffel builds a huge tower in Paris, calls it the Eiffel tower. Alexander the Great conquers twenty foreign nations, founds twenty cities called Alexandria. Every scientist with a famous formula. Every father who's ever named their kid 'Junior'. How many buildings, bridges, ships, metropolises, states, and people are named after some dead guy? It's not because they were conceited or unoriginal, it's self-eponynism. It's because the only way to live forever is to find something really big, and put your name on it.

Are they not the world's most legendary graffiti artists? They never had to steal a can of paint, or crawl under a chain link fence, or run from the cops, or do community service. But I'm sure they laid awake at night with the same fear of being forgotten that he had. They all figured it out. Like Derrick, they all realized their own temporality, and found the solution. They just didn't have to get caught to become a `legend'.




\end{document}
