\documentclass{article}

\usepackage{fullpage}   % Use the whole page
\usepackage{fancyhdr}   % Nice headers/footers
\usepackage{mdwlist}    % For itemize* and enumerate*
\usepackage{hyperref}   % Hyperlink references and URLs

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={ServiceSniffer Software Requirements Specification v2},
    pdfauthor={Justin Courts; Philip Cristiano; Charles Rumford; Thomas Wambold}
}

% So we can number paragraphs too
\setcounter{secnumdepth}{1}

% For headers and footers
\setlength{\headheight}{15pt}
\setlength{\headsep}{25pt}
\pagestyle{fancy}
	
% Page style for the title page
\fancypagestyle{plain}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
}

% Just so we don't have to specify this twice
\newcommand\mytitle{Peer Review for Team 2 \\ \large{Reviewed by Team 11}}
\newcommand\mydate{January 19, 2010}

% Page style for every other page
\fancyhf{} % clear all header and footer fields
\fancyhead[L]{ServiceSniffer}
\fancyhead[C]{\mytitle}
\fancyhead[R]{\mydate}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\title{\textbf{\mytitle}}
\author{
    Justin Courts \\\url{justin@servicesniffer.net}
    \and Philip Cristiano \\\url{phil@servicesniffer.net}
    \and Charles Rumford \\\url{charlesr@servicesniffer.net}
    \and Thomas Wambold \\\url{tom@servicesniffer.net}
}
\date{\mydate}

\begin{document}
\maketitle

%------------------------------------------------------------------------------

\section{Requirements Document}

\subsection{Document-wide}

\begin{itemize}
    \item Lots of use of they/them/their/etc. in singular context.  
    \item Move Definition of Roles and Glossary to the top of the document,
        where they're most useful.  Also, include more terms (like Stream) -
        all terms that are unique or otherwise specific to this system.
\end{itemize}

%------------------------------------------------------------------------------

\subsection{1 Abstract}

\begin{itemize}
    \item Refer to your project by name at least once
    \item 4th generation phones? Doesn't really seem clear as to what a 4th
        generation phone is although 4g networks makes sense, I've never heard
        to it as 4th generation phone.
    \item Minor thing, if you are using \LaTeX\ (it looks like you are) you can
        use the ``abstract'' environment instead of a section to get a nicely
        formatted abstract.  Like this:
    \begin{verbatim}
    \begin{abstract}
       ...
    \end{abstract}
    \end{verbatim}
\end{itemize}

%------------------------------------------------------------------------------

\subsection{2 Introduction}

\subsubsection{2.1 Purpose}

\begin{itemize}
    \item Seems weird to have a 2.1 heading when there's no 2.2 or more.  Add
        another heading, or combine this all under simple ``2 Introduction''?
    \item ``not only for audio communication, but video streaming as well''
        $\rightarrow$ ``[\dots] but also for video streaming as well'' --
        parallelism and not only/but also.  Also, remove the comma before
        ``but'' as it's not needed (dependent clause)
    \item ``provide one with'' sounds weird here.  ``provides
              consumers/users/something with''?
    \item ``This document outline [\dots]'' $\rightarrow$ ``outlines''
    \item ``[\dots] that such as system [\dots]'' $\rightarrow$ ``a system''
\end{itemize}

%------------------------------------------------------------------------------

\subsection{3 Functional Requirement}

\subsubsection{3.1 Client}

\paragraph{3.1.1 Video Streaming Service}

\begin{itemize}
    \item 3.1.1.1  Pause and Un-Pause
    \begin{itemize}
        \item Does pausing cause the data to be buffered to send after being
            unpaused, or just pick up streaming in realtime?
        \item What type of user notification is there that the stream if being
            paused?
        \item What does it mean to disconnect?
        \item What is the relationship between the client and the server in
        regards to stream?
        \item Why can't I pause a stream with audio?
    \end{itemize}
    \item 3.1.1.3  Volume Control
    \begin{itemize}
        \item Does the volume control have any effect on the audio being sent
            to the server?  Is there a way to mute on the Video Streaming
            Screen?
        \item What's the default?
    \end{itemize}
    \item 3.1.1.4  Logout
    \begin{itemize}
        \item Is there a confirmation screen for this?
        \item Is there any way to be automatically logged out, like timeout,
            disconnection, etc?
        \item Is logout the right word or you just want to suspend streaming.
            Will they no longer be able to use the app if they have surpassed
            their quota?  How can they remove any video if they cannot log in
            again?
    \end{itemize}
    \item 3.1.1.5 Storage
    \begin{itemize}
        \item What is tho storage for?
        \item Is there an easy way to clean out the storage?
    \end{itemize}
\end{itemize}

%------------------------------------------------------------------------------

\paragraph{3.1.2 Credentials Management Screen}

\begin{itemize}
    \item 3.1.2.1 Username --- Max/min length?  Bad characters?  Case
        matters?
    \item 3.1.2.2 Password --- Max/min length?  Bad characters?  Case
        matters?
    \item 3.1.2.3 Store Credentials --- No confirmation or way to cancel?
    \item 3.1.2.4  Login
    \begin{itemize}
        \item ``loging'' $\rightarrow$ ``logging''
        \item ``begining'' $\rightarrow$ ``beginning''
        \item ``will, if necessary, initiate cause credentials to be stored''
            $\rightarrow$ initiate or cause, but not both
        \item ``logic'' $\rightarrow$ ``login''
    \end{itemize}
\end{itemize}

%------------------------------------------------------------------------------

\paragraph{3.1.4 Update on Login}

Updates for login. You may want to have a minimal acceptable version.  During
an emergency you may not want to require software updates in every case.

%------------------------------------------------------------------------------

\subsubsection{3.2 Server}

\paragraph{3.2.1 Login Page} Security type/details?

%------------------------------------------------------------------------------

\paragraph{3.2.3 Download Page} What browser?  All?  Any?  The default?  A
    specific one you dictate?

%------------------------------------------------------------------------------

\paragraph{3.2.4 Sidebar Navigation}
\subparagraph{3.2.4.3  Recently Viewed Slices} up to 5 slices
\subparagraph{3.2.4.5  My Adopted Slices} up to 5 slices

%------------------------------------------------------------------------------

\paragraph{3.2.5 Main Page}

\subparagraph{3.2.5.2 Search} Capitalize "The" (first word in paragraph)

%------------------------------------------------------------------------------

\paragraph{3.2.6 View Slices Page}

\subparagraph{3.2.6.4 Two Way Audio Controls}
    Are Two Way audio conversations recorded with each slice?  If so, can you
    record without the audio?
\subparagraph{3.2.6.5 Exit Button}
    Confirmation box?

%------------------------------------------------------------------------------

\paragraph{3.2.7 Slice Edit Page}

\begin{itemize}
    \item Moderator hasn't been defined, I don't think.  
    \item "to modify or to delete" is ambiguous -- either option needs to be
        available, or users should be allowed to pick either option?
\end{itemize}

%------------------------------------------------------------------------------

\paragraph{3.2.8 User Settings Page}
\subparagraph{3.2.8.1  Change Password}
    Be clearer as to whether the newly typed password is the new password to be
    set.  I know it is, but it should be clearer in the document to avoid any
    ambiguity
\subparagraph{3.2.8.2  Change Email Address}
    Same as with Change Password above

%------------------------------------------------------------------------------

\paragraph{3.2.9  User Management Page}
\begin{itemize}
    \item Random password:  What parameters?  Length/Characters/etc
    \item Is this new password only available for a certain timeframe?
    \item Must this password be changed on next login, or is it permanent?
    \item You shouldn't send passwords via email. Send a new link to the user
        to allow them to reset a password.  Considering the time taken to
        mention encryption everywhere else it would be bad to send it via
        plaintext.
\end{itemize}

%------------------------------------------------------------------------------

\subsection{4 Non-Functional Requirements}

\paragraph{4.1  Security}
\subparagraph{4.1.1  Stream Encryption}
    What type of encryption?
\subparagraph{4.1.2  Server Login/Sign-Up Encryption}
    What type of encryption?
\subparagraph{4.1.3  Client Login Encryption}
    What type of encryption?

%------------------------------------------------------------------------------

\paragraph{4.2 Client Platform Requirements}
    The numbering below is off (4.2.0.1 should be 4.2.1, etc.)
\subparagraph{4.2.0.1  Operating System}
    What versions?  All?
\subparagraph{4.2.0.2  Camera}
    Can all Android cameras record video?
\subparagraph{4.2.0.4  Speaker}
    Speaker as in speaker phone, or would a normal headset speaker work?
\subparagraph{4.2.0.6  Connectivity}
    List protocols

%------------------------------------------------------------------------------

\paragraph{4.3  Server Platform Requirements}
    What version of Firefox, and what version of Java?  If no specific
    versions, which minimum versions?

%------------------------------------------------------------------------------

\paragraph{4.5  Client Configuration}
    The numbering below is off (4.5.0.1 should be 4.5.1, etc.)
\subparagraph{4.5.0.3  Server Settings}
    What happens if the settings are missing or wrong?
\subparagraph{4.5.0.4  GPS Updates}
    \begin{itemize}
        \item Units?
        \item You mention using GPS but don't have it as a requirement for the
        client. Will you also use trilateralization of cell sites? I know it's
        built into Blackberry OS, not sure about Android, but the API is the
        same you just have to specify precision if you want to use GPS.
        \item Your 10 foot limit is with in the 3m accuracy of GPS. You will
        get false movement.
    \end{itemize}
\subparagraph{4.5.0.5  Lost Data Limit}
    Default?  Metric used for this (e.g. dropped packets over a rolling minute
    window)?

%------------------------------------------------------------------------------

\paragraph{4.6  Server Configuration}
    The numbering below is off (4.6.0.6 should be 4.6.1, etc.)
\subparagraph{4.6.0.6  Max Incoming Streams}
    Are they queued or rejected?
\subparagraph{4.6.0.7  Max Outgoing Streams}
    Are they queued or rejected?
\subparagraph{4.6.0.8  User Space Quota}
    No message?
\subparagraph{4.6.0.10  User Sign-Up Approval}
    Approval at what level?  Email approval?  Moderator approval?
    Administrator approval?
\subparagraph{4.6.0.11  Account Requires Valid Email Address}
    What if someone changes an email address incorrectly?  They're locked out
    for good? (``The system must allow a User to login only after he/she has
    clicked on the verification link.'') --- the last two sentences are unclear
    how the system will work for an email change.

%------------------------------------------------------------------------------

\paragraph{4.7  Video-Audio-GPS Stream}
\begin{itemize}
    \item The numbering below is off (4.7.0.12 should be 4.7.1, etc.)
    \item What happens if the stream doesn't hold up to 720*480 @ 30fps?
    \item 720x480x30 seems quite high for mobile streaming. Do you know that that
works?
    \item You will find that this is a lot of data to push over WiMax,
    especially with no multicast support.
\end{itemize}

%------------------------------------------------------------------------------

\subsubsection{5  System Evolution}
\paragraph{5.1  Multiple Tags from Multiple Users}
\begin{itemize}
    \item ``furture'' $\rightarrow$ ``future''
    \item ``tages'' $\rightarrow$ ``tags''
\end{itemize}
\paragraph{5.2  Comments System}
    Remove the comma after ``slice''
\paragraph{5.7  Buffer Failed Data}
    Because it was dropped?  Because it was paused?  Both?

%------------------------------------------------------------------------------

\section{Acceptance Test Plan}

\subsection{Document-wide}

\begin{itemize}
    \item Not a big change, but I suggest making every single test individual
        subheadings (so instead of, for example, 1.4.1 \#13 you have 1.4.1.13).
        It'll make it easier to reference on failure/success
    \item Not "should" but "shall"
    \item Otherwise, pretty complete and good.  Just some small points below:
\end{itemize}

%------------------------------------------------------------------------------

\subsection{1 Client Application}

\paragraph{1.1  Custom Client Build}
    What process included with the system?

%------------------------------------------------------------------------------

\subsection{2 Server Application}
\subparagraph{2.3.3  Approval Required}
    I suggest more detail here, like ``the same Sign-Up tests'' --- refer to them
    by section number.  Also, ``Approve the user'' is meaningless without
    reference or explanation.

\paragraph{2.4  Log-In Page}
    Testing server?  To the index page of the default site?  To something
    specific?  Give an example.

\end{document}
