\newcommand{\defn}[2]{\paragraph{#1}{#2}}
\section{Introduction}
\subsection{Purpose}
The purpose of this document is to explain all necessary requirements for Windmill's chess software in the
IEEE standard. This include functional, non-functional, constraints, use case specifications, and graphical prototypes
of our chess software.

\subsection{Scope}
This document is the initial version (1.0) of the requirements specifications for Windmill's chess software. Software
developers and testers are the intended readers of this document.

\subsection{Definition, Acronyms, and Abbreviations}
\defn{Bishop}{One of six chess pieces in a chess game. It is permitted to only move in a diagonal direction on a
chessboard.}
\defn{Checkmate}{A chess game state wherein one player's king will be inevitably captured.}
\defn{Chess}{A board game played between two players on a chess board with sixty four squares. Each square may hold only
one chess piece.}
\defn{GUI}{Acronym for Graphical User Interface. It provides a graphical front end for computer programs.}
\defn{Internet}{A large worldwide system of connected networks.}
\defn{IP Address}{Unique 32-bit number that identifies any computer connected to the Internet.}
\defn{Port}{A 16-bit number that indicates a communication channel on a specific machine.}
\defn{Java}{An object oriented computer programming language.}
\defn{King}{One of six chess pieces in a chess game. Each player receives one king at the start of the chess game. It can
move in any direction on a chessboard. The objective in a chess game is to protect it from capture by the opponent.}
\defn{Knight}{One of six chess pieces in a chess game. Each player receives two knights at the start of the chess game. It
moves in two possible unique ways, two horizontally and one vertically or vice versa.}
\defn{Queen}{One of six chess pieces in a chess game. Each player receives one queen at the start of the chess game. In a
chess game, it can move in any direction.}
\defn{Rook}{One of six chess pieces in a chess game. Each player receives two rooks at the start of the chess game. It can
move either horizontally or vertically any number of squares.}
\defn{Swing}{An API library for providing a GUI to Java programs.}
\defn{Thread}{Code that runs within the address space of a single process.}

\subsection{Overview}
Following this introduction, an overall description, use case diagrams, non-functional and functional requirements, and graphical user
interface prototypes are presented.

